\LARGE Coursework \\ Module Name (CMM536)

### 2018-04-27 submission.tex
graphics added

\title{\LARGE Coursework  \\ Module Name (CMM...)}

\author{Your Name, \textit{\href{email@rgu.ac.uk}{email@rgu.ac.uk}}}
\maketitle
% \begin{flushleft} \today \end{flushleft} 
\noindent\rule{16cm}{0.4pt}
%\underline{\hspace{3cm}
\ \\
%\thispagestyle{empty}

@@

[your text goes here]
The paper that was chosen for this work is \cite{6779381}. The authors provided a full review on different streaming algorithms and methos that handle concept drfit?. Below is a review of this paper that includes problem statement, related work and methods applied.\\

\textcolor{blue}{\textit{Notice how I cited the paper, and how does it appear in the document, to do so, you need to have a file in your working director (references.bib), this file simply contains the bibtext items for the papers you chose. These BibTex items are often avaiable to download from publishers website, see Figure~\ref{fig1}}}
\subsection{Problem Statement}

@@

\subsection{Relevant Work}
The paper acknowleges previous studies \emph{Haffner2005} \emph{Raahemi2008}  \emph{Zander2005} which were able to classify messaging data through the port number, protocol signature and protocol type. However, these methods are not applicable for encrypted data. Later studies \emph{Huanhuan2005} \emph{Fu2016}, including one by the same team \emph{Fu2016}, were able to classify encrypted data using machine learning by segmenting traffic and then classifying it. These attempts suffered from low relative accuracy and speed.

@@

-TODO citations

@@

Here, a parameter grid is defined and stored as a dataframe to be accessed as each candidate model is trained
\begin{Schunk}
\begin{Sinput}
> num_attributes <- ncol(df_train)
> #build a parameter grid
> # Random forest
> mtry <- as.integer(c(num_attributes * 0.25, num_attributes / 3, num_attributes * 0.5, num_attributes * 0.8))
> nodesize <- c( 3, 5, 20)
> ntree <- c(200)
> PG<- as.data.frame(expand.grid(mtry=mtry, nodesize=nodesize,
+                                          ntree=ntree, stringsAsFactors=F))
\end{Sinput}
\end{Schunk}
Now, we train up a random forest on the training set for each combination of parameters in the parameter grid. \\
For each combination of parameters, the resulting model is tested on the evaluation set and the accuracy calculated.
The resulting accuracy from each parameter combination is saved in the 'Accuracy' column of the parameter grid table:
\begin{Schunk}
\begin{Sinput}
> for (i in c(1:nrow(PG))){
+   mtry <- PG[i, "mtry"]
+   nodesize <- PG[i, "nodesize"]
+   ntree <- PG[i, "ntree"]
+ 
+   temp_model <- randomForest(formula(df_train) , data=df_train, mtry=mtry, ntree=ntree, nodesize=nodesize)
+   predictions <- predict(temp_model , df_valid)
+   cm<- confusionMatrix(predictions,df_valid$won)
+   accuracy <- cm$overall['Accuracy']
+   PG[i,'Accuracy'] <- accuracy
+   print(i)
+ }
\end{Sinput}
\end{Schunk}

The parameters which produced the best model are selected and that model is evaluated on the testing set to give a final accuracy for the random forest classifier.
\begin{Schunk}
\begin{Sinput}
> #assess best model on test set
> PG <- PG%>%
+   arrange(desc(Accuracy))
> mtry <- PG[1, "mtry"]
> nodesize <- PG[1, "nodesize"]
> ntree <- PG[1, "ntree"]
> best_model <- randomForest(formula(df_train) , data=df_train, mtry=mtry, ntree=ntree, nodesize=nodesize , importance=T)
> predictions <- predict(temp_model , df_valid)
> confusionMatrix(predictions,df_valid$won)
\end{Sinput}
\end{Schunk}
TODO - discuss the results
    - variable importances
    -data diagram

@@

A validation set will not be used in this case since the aim is to demonstrate a streaming classifier; parameter tuning was demonstrated in the above section. So, the validation and testing set from the above section are combined to create a new testing set. The stream classifier will therefore be trained on 60\% of the original dataset:
\begin{Schunk}
\begin{Sinput}
> df_test <- bind_rows(df_test,df_valid)
> 
\end{Sinput}
\end{Schunk}
Several classifier types were tried but that which gave the quickest improvement in accuracy was the 'Ozaboost' classifier. This is a boosted model created specifically for streaming. A Hoeffding tree is used as the base learner.
\begin{Schunk}
\begin{Sinput}
> mymodel <- OzaBoost(baseLearner="trees.HoeffdingTree", ensemblesize=30)
\end{Sinput}
\end{Schunk}
A stream object is created to pass the data incrementally to the model. It was decided to stream data in chunks of 100 instances. For the training set of ~60000 rows, this will give ~600 chunks overall. The dataset has over 100 dimensions so 100 rows should contain enough data for the model to meaningfully update itself on every iteration.
\begin{Schunk}
\begin{Sinput}
> # Create a stream 
> dfStream <-datastream_dataframe(data=as.data.table(df_train))
> # other variables for training
> chunk <- 100
> #use the chunk size and size of the training set to define the number of turns required for training
> turns <- (nrow(dfStream$data)/chunk)-1
> turns <- floor(turns)
\end{Sinput}
\end{Schunk}
We make a similar stream object for the testing data. This will allow for testing concurrent to training ie, the model will be tested after every training iteration. This will allow for early stopping if a desired accuracy is reached before the full dataset has been used for training.\\
Note, the size of the testing chunks is defined by taking the size of the training chunks and scaling it down in proportion to the test/training set size. This ensures there are an equal number of training and testing chunks, so testing can be carried out after every training iteration.
\begin{Schunk}
\begin{Sinput}
> #make a test stream
> test_stream <- datastream_dataframe(data=as.data.table(df_test))
> # other variables for testing
> test_chunk <- floor(100 / (nrow(df_train)/nrow(df_test)))
\end{Sinput}
\end{Schunk}
Training is performed on a single chunk of data. This is achieved by retrieving a chunk from the stream object. The chunk is then used as training data for the model defined above:
\begin{Schunk}
\begin{Sinput}
> ## first sample (train) - retrieves first 100 records ##
> sample <- dfStream$get_points(dfStream, n = chunk,
+                               outofpoints = c("stop", "warn", "ignore"))
> ## Train the first chunk
> myboostedclassifier <- trainMOA(model = mymodel,
+                                 formula = won ~.,
+                                 data = datastream_dataframe(sample))
\end{Sinput}
\end{Schunk}
A single chunk of test data is also taken to be used for testing on this initial training iteration:
\begin{Schunk}
\begin{Sinput}
> test_sample <- test_stream$get_points(test_stream, n = test_chunk,
+                                       outofpoints = c("stop", "warn", "ignore"))
\end{Sinput}
\end{Schunk}
The test sample is used to evaluate the accuracy of the initial training run:
\begin{Schunk}
\begin{Sinput}
> ## Do some prediction to test the model
> predictions <- predict(myboostedclassifier, test_sample)
> table(sprintf("Actuals: %s", test_sample$won),
+       sprintf("Predicted: %s", predictions))
\end{Sinput}
\begin{Soutput}
              Predicted: -1 Predicted: 1
  Actuals: -1            17           13
  Actuals: 1             20           15
\end{Soutput}
\begin{Sinput}
> # calculate accuracy
> cat("Accuracy is: ", sum(predictions==test_sample$won)/nrow(test_sample)*100,"%")
\end{Sinput}
\begin{Soutput}
Accuracy is:  49.23077 %
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> library(dplyr)
> library(tm)
> library(SnowballC)
> library(RColorBrewer)
> library(wordcloud)
> library(ggplot2)
> library(gridExtra)
> library(graph)
> library(Rgraphviz)
> library(RTextTools)
> df <- read.csv("leaveRemainTweets_CW.csv")
\end{Sinput}
\end{Schunk}
The 'leave' and 'remain' tweets are seperated and stored in different objects. We also check that we have captured all tweets by seperating by label (ie there a no unlabelled tweets, or any with labels outwith 'leave' or 'remain'):
\begin{Schunk}
\begin{Sinput}
> #seperate dataframes for leave and remain tweets
> leave_tweets <- df%>%
+   filter(label=="Leave")
> remain_tweets <- df%>%
+   filter(label=="Remain")
> #check we have captured all the tweets
> nrow(df)==(nrow(leave_tweets) + nrow(remain_tweets))
\end{Sinput}
\begin{Soutput}
[1] TRUE
\end{Soutput}
\end{Schunk}
It is important to ensure the dataset is balanced, ie there are a similar number of leave and remain tweets. This is indeed the case:
\begin{Schunk}
\begin{Sinput}
> nrow(leave_tweets)
\end{Sinput}
\begin{Soutput}
[1] 1254
\end{Soutput}
\begin{Sinput}
> nrow(remain_tweets)
\end{Sinput}
\begin{Soutput}
[1] 1029
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> #make wordclouds from the frequency tables
> make_wordcloud(remain$freq_tab)
\end{Sinput}
\end{Schunk}
\includegraphics{submission-028}

@@

\begin{figure}[H]
\begin{center}
\begin{Schunk}
\begin{Sinput}
> make_wordcloud(leave$freq_tab)
\end{Sinput}
\end{Schunk}
\includegraphics{submission-029}
\caption {Wordclouds for the leave tweets}
\label{fig11}
\end {center}
\end {figure}

In addition to wordclouds, we can plot the most common words for each class of tweet. This is achieve with the function below:
\begin{Schunk}
\begin{Sinput}
> #function to plot wordclouds
> plot_wordcount <- function(freq_tab,title_text){
+   ggplot(head(freq_tab,20), aes(x=word,y=freq))+
+     geom_bar(stat="identity")+
+     labs(title=title_text)+
+     theme(axis.text.x = element_text(angle = 30, hjust = 1))
+ }
> a<-plot_wordcount(all_tweets$freq_table,"most common words for all tweets")
> b<-plot_wordcount(remain$freq_table,"most common words for remain tweets")
> c<-plot_wordcount(leave$freq_table,"most common words for leave tweets")
\end{Sinput}
\end{Schunk}
The most common word for leave tweeters was 'June', suggesting many of them were focused on reinforcing the timing of the referendum - ensuring people remembered to go out and vote. 'via', 'spread' and 'word' were also common, suggesting attempts to get readers to spread the message. The general theme of many of the common words for leave tweets is of trying to increase virality and therefore increase re-tweets.\\
The most common word for remain tweeters was 'say', followed by 'stay', 'will' and 'bori[s]'. These give less of an impression of a common theme compared to the leave tweets. It is not surprising that 'Boris' is mentioned a lot by the remain tweeters since he proved to be a particularly divisive figure during the campaigning. However, the lack of common theme for leave tweets may point to an overall less coordinated campaign and may have been a contributary factor to the final result of the referendum (this is just conjecture however - it must be stressed that the dataset forms a small minority of all tweets from the campaign period).\\
As a humorous aside 'brexitthemovi[e]' was in the top 20 most common words. I don't remember this term from the campaign period but it is interesting to see such a specific term become so popular.

\begin{figure}[H]
\begin{center}
\begin{Schunk}
\begin{Sinput}
> grid.arrange(a,b,c, nrow = 3)
\end{Sinput}
\end{Schunk}
\includegraphics{submission-031}
\caption {Wordcounts for the tweets}
\label{fig10}
\end {center}
\end {figure}

@@

\begin{figure}[H]
\begin{center}
\begin{Schunk}
\begin{Sinput}
> plot(remain$tdm, term = findFreqTerms(remain$tdm, lowfreq = 10), corThreshold = 0.1,
+      weighting = T, main="word association for remain tweets")
\end{Sinput}
\end{Schunk}
\includegraphics{submission-032}
\caption {Word association for remain tweets}
\label{fig12}
\end {center}
\end {figure}

The leave tweets on the other hand show some strongly associated words. As suspected previously 'spread', 'word' and 'via' are strongly associated. This suggests a coordinated effort to increase virality of these tweets and make them more visible. 
'Take back control' is another strong grouping. This is a strong and positivley phrased phrase  which would be likely to grab and hold readers' attention (whether we agree with it or not). This contrasts with the negative phrases from the remain tweets which, rather than focusing on why readers should vote remain, seemed more to focus on why readers should \emph{not} vote leave.
Finally 'Cameron', 'Send' and 'Speech' were strongly associated. The reason for this is a little more difficult to ascertain but may relate to one of Cameron's campaign speeches or debates which generally proved to be divisive at the time.
\begin{figure}[H]
\begin{center}
\begin{Schunk}
\begin{Sinput}
> plot(leave$tdm, term = findFreqTerms(leave$tdm, lowfreq = 15), corThreshold = 0.1,
+      weighting = T, main="word association for leave tweets")
\end{Sinput}
\end{Schunk}
\includegraphics{submission-033}
\caption {Word association for leave tweets}
\label{fig12}
\end {center}
\end {figure}

@@

\begin{Schunk}
\begin{Sinput}
> #transpose the dtm to get word count for each tweet
> dtm<-make_tdm(df$text,10)
> dtm<-dtm$dtm
> #checknumber of columns used for model
> ncol(as.matrix(dtm))
\end{Sinput}
\begin{Soutput}
[1] 87
\end{Soutput}
\end{Schunk}
Using the RTextTools package, the tweets are saved in a container-type object. This automatically performs a train-test split. In this case the training set forms 70\% of the data:
\begin{Schunk}
\begin{Sinput}
> container <- create_container(dtm, as.numeric(factor(df$label)),trainSize=1:round(0.7*nrow(df)), testSize=(round(0.7*nrow(df))+1):nrow(df),virgin=FALSE)
> 
\end{Sinput}
\end{Schunk}
A number of classification models are trained on the data, and evaluated on the test set. RTextTools automatically creates results and analytics objects which we can use to evaluate model performance:
\begin{Schunk}
\begin{Sinput}
> #train some models and se what we get
> models <- train_models(container,algorithms=c("SVM","TREE","BAGGING","BOOSTING","RF"))
> results <- classify_models(container, models) #can use for conf matrix
> analytics <- create_analytics(container, results)
\end{Sinput}
\end{Schunk}

>>>>

\title{\LARGE Coursework  \\ Module Name (CMM536)}

\author{Alexander Hall, \textit{\href{1608941@rgu.ac.uk}{1608941@rgu.ac.uk}}}
\maketitle
% \begin{flushleft} \today \end{flushleft} 
\noindent\rule{16cm}{0.4pt}
%\underline{\hspace{3cm}
\ \\
%\thispagestyle{empty}

@@

The paper that was chosen for this work is \cite{Liu:2017:ERI:3097983.3098049}. The authors attempted to improve methods for classifying encrypted messaging traffic through streaming methods. Below is a review of this paper that includes problem statement, related work and methods applied.\\

\subsection{Problem Statement}

@@

\subsection{Relevant Work}
The paper acknowleges previous studies \emph{Haffner:2005:AAC:1080173.1080183} \cite{4669733}  \emph{1550864} which were able to classify messaging data through the port number, protocol signature and protocol type. However, these methods are not applicable for encrypted data. Later studies \cite{5693957}, including one by the same team \cite{7377112}, were able to classify encrypted data using machine learning by segmenting traffic and then classifying it. These attempts suffered from low relative accuracy and speed.

@@

@@

Here, a parameter grid is defined and stored as a dataframe to be accessed as each candidate model is trained
\begin{Schunk}
\begin{Sinput}
> num_attributes <- ncol(df_train)
> #build a parameter grid
> # Random forest
> mtry <- as.integer(c(num_attributes * 0.25, num_attributes / 3, num_attributes * 0.5, num_attributes * 0.8))
> nodesize <- c( 3, 5, 20)
> ntree <- c(200)
> PG<- as.data.frame(expand.grid(mtry=mtry, nodesize=nodesize,
+                                          ntree=ntree, stringsAsFactors=F))
\end{Sinput}
\end{Schunk}
Now, we train up a random forest on the training set for each combination of parameters in the parameter grid. \\
For each combination of parameters, the resulting model is tested on the evaluation set and the accuracy calculated.
The resulting accuracy from each parameter combination is saved in the 'Accuracy' column of the parameter grid table:
\begin{Schunk}
\begin{Sinput}
> for (i in c(1:nrow(PG))){
+   mtry <- PG[i, "mtry"]
+   nodesize <- PG[i, "nodesize"]
+   ntree <- PG[i, "ntree"]
+ 
+   temp_model <- randomForest(formula(df_train) , data=df_train, mtry=mtry, ntree=ntree, nodesize=nodesize)
+   predictions <- predict(temp_model , df_valid)
+   cm<- confusionMatrix(predictions,df_valid$won)
+   accuracy <- cm$overall['Accuracy']
+   PG[i,'Accuracy'] <- accuracy
+   print(i)
+ }
\end{Sinput}
\begin{Soutput}
[1] 1
[1] 2
[1] 3
[1] 4
[1] 5
[1] 6
[1] 7
[1] 8
[1] 9
[1] 10
[1] 11
[1] 12
\end{Soutput}
\end{Schunk}

The parameters which produced the best model are selected and that model is evaluated on the testing set to give a final accuracy for the random forest classifier.
\begin{Schunk}
\begin{Sinput}
> #assess best model on test set
> PG <- PG%>%
+   arrange(desc(Accuracy))
> mtry <- PG[1, "mtry"]
> nodesize <- PG[1, "nodesize"]
> ntree <- PG[1, "ntree"]
> best_model <- randomForest(formula(df_train) , data=df_train, mtry=mtry, ntree=ntree, nodesize=nodesize , importance=T)
> predictions <- predict(temp_model , df_valid)
> confusionMatrix(predictions,df_valid$won)
\end{Sinput}
\begin{Soutput}
Confusion Matrix and Statistics

          Reference
Prediction   -1    1
        -1 4019 3194
        1  5548 7442

               Accuracy : 0.5673          
                 95% CI : (0.5604, 0.5741)
    No Information Rate : 0.5265          
    P-Value [Acc > NIR] : < 2.2e-16

                  Kappa : 0.1213          
 Mcnemar's Test P-Value : < 2.2e-16

            Sensitivity : 0.4201          
            Specificity : 0.6997          
         Pos Pred Value : 0.5572          
         Neg Pred Value : 0.5729          
             Prevalence : 0.4735          
         Detection Rate : 0.1989          
   Detection Prevalence : 0.3570          
      Balanced Accuracy : 0.5599

       'Positive' Class : -1              
\end{Soutput}
\end{Schunk}
TODO - discuss the results
    - variable importances
    -data diagram

@@

A validation set will not be used in this case since the aim is to demonstrate a streaming classifier; parameter tuning was demonstrated in the above section. So, the validation and testing set from the above section are combined to create a new testing set. The stream classifier will therefore be trained on 60\% of the original dataset:
\begin{Schunk}
\begin{Sinput}
> df_test <- bind_rows(df_test,df_valid)
> 
\end{Sinput}
\end{Schunk}
Several classifier types were tried but that which gave the quickest improvement in accuracy was the 'Ozaboost' classifier. This is a boosted model created specifically for streaming. A Hoeffding tree is used as the base learner.
\begin{Schunk}
\begin{Sinput}
> mymodel <- OzaBoost(baseLearner="trees.HoeffdingTree", ensemblesize=30)
\end{Sinput}
\end{Schunk}
A stream object is created to pass the data incrementally to the model. It was decided to stream data in chunks of 100 instances. For the training set of ~60000 rows, this will give ~600 chunks overall. The dataset has over 100 dimensions so 100 rows should contain enough data for the model to meaningfully update itself on every iteration.
\begin{Schunk}
\begin{Sinput}
> # Create a stream 
> dfStream <-datastream_dataframe(data=as.data.table(df_train))
> # other variables for training
> chunk <- 100
> #use the chunk size and size of the training set to define the number of turns required for training
> turns <- (nrow(dfStream$data)/chunk)-1
> turns <- floor(turns)
\end{Sinput}
\end{Schunk}
We make a similar stream object for the testing data. This will allow for testing concurrent to training ie, the model will be tested after every training iteration. This will allow for early stopping if a desired accuracy is reached before the full dataset has been used for training.\\
Note, the size of the testing chunks is defined by taking the size of the training chunks and scaling it down in proportion to the test/training set size. This ensures there are an equal number of training and testing chunks, so testing can be carried out after every training iteration.
\begin{Schunk}
\begin{Sinput}
> #make a test stream
> test_stream <- datastream_dataframe(data=as.data.table(df_test))
> # other variables for testing
> test_chunk <- floor(100 / (nrow(df_train)/nrow(df_test)))
\end{Sinput}
\end{Schunk}
Training is performed on a single chunk of data. This is achieved by retrieving a chunk from the stream object. The chunk is then used as training data for the model defined above:
\begin{Schunk}
\begin{Sinput}
> ## first sample (train) - retrieves first 100 records ##
> set.seed(57)
> sample <- dfStream$get_points(dfStream, n = chunk,
+                               outofpoints = c("stop", "warn", "ignore"))
> ## Train the first chunk
> 
> myboostedclassifier <- trainMOA(model = mymodel,
+                                 formula = won ~.,
+                                 data = datastream_dataframe(sample))
\end{Sinput}
\end{Schunk}
A single chunk of test data is also taken to be used for testing on this initial training iteration:
\begin{Schunk}
\begin{Sinput}
> test_sample <- test_stream$get_points(test_stream, n = test_chunk,
+                                       outofpoints = c("stop", "warn", "ignore"))
\end{Sinput}
\end{Schunk}
The test sample is used to evaluate the accuracy of the initial training run. It is as good as random guessing, so unsurprisingly more data will be required to build a useful classifier:
\begin{Schunk}
\begin{Sinput}
> ## Do some prediction to test the model
> predictions <- predict(myboostedclassifier, test_sample)
> table(sprintf("Actuals: %s", test_sample$won),
+       sprintf("Predicted: %s", predictions))
\end{Sinput}
\begin{Soutput}
              Predicted: -1 Predicted: 1
  Actuals: -1            17           13
  Actuals: 1             20           15
\end{Soutput}
\begin{Sinput}
> # calculate accuracy
> cat("Accuracy is: ", sum(predictions==test_sample$won)/nrow(test_sample)*100,"%")
\end{Sinput}
\begin{Soutput}
Accuracy is:  49.23077 %
\end{Soutput}
\end{Schunk}
The results for each training/testing iteration will be held in a vector for later analysis:
\begin{Schunk}
\begin{Sinput}
> # hold results in a vector
> accuracies <- c()
> #reset the test stream 
> test_stream$reset()
\end{Sinput}
\end{Schunk}
Now the model is incrementally trained and tested by feeding in chunks sequentially. For each iteration a training chunk is presented and the model is incrementally trained on that chunk. Then a testing chunk is presented to assess the performance of the model for each iteration, printing the current accuracy to the console. \textit{Full output not included in this document for brevity}.

\begin{Schunk}
\begin{Sinput}
>#train over the stream
>for (i in 1:turns){
>  # next sample
> sample <- dfStream$get_points(dfStream, n = chunk,
+                               outofpoints = c("stop", "warn", "ignore"))
>  test_sample <- test_stream$get_points(test_stream, n = test_chunk,
+                                       outofpoints = c("stop", "warn", "ignore"))
>  ## Update the trained model with the new chunks
>  myboostedclassifier <- trainMOA(model = myboostedclassifier$model,
+                                  formula = won ~ .,
+                                  data = datastream_dataframe(sample),
+                                  reset = FALSE,trace = FALSE)
>  cat("chunk: ",i,"\n")

>  predictions <- predict(myboostedclassifier, test_sample)
>  # calculate accuracy
>  accuracies[i] <- sum(predictions==test_sample$won)/nrow(test_sample)*100
>  if(i %% 100 = 0){
>  cat("chunk ",i," accuracy = ",accuracies[i],"%","\n")
>  }
>}

\end{Sinput}
\end{Schunk}

The final accuracy achieved was 58.1\%, which is actually higher than for the best non-streaming model. This may be due to the use of a different model type which performed better on the given dataset. This is also a reasonably high accuracy for this problem - as stated earlier, anything above 50\% is considered a positive result since an ideal game should be perfectly balanced.

The improvement in accuracy with training/testing iteration is plotted below. We see that the classifier was rather erratic in accuracy as more data was presented to it. The general trend was for accuracy to steadily increase, although peak accuracy was reached aroumd chunk 350, suggesting only about half the data was required to fit a model. However, accuracy was increasing towards the end of the streaming process, so a larger dataset may have given even better results.

\begin{Schunk}
\begin{Sinput}
>accuracies <- as.data.frame(accuracies)
>ggplot(accuracies,aes(y=accuracies,x=seq(1,length(accuracies))))+
+  geom_line(col="blue",alpha=0.7)+
+ geom_smooth(method="lm",col="red")+
+  labs(title="accuracy of streaming classifier",subtitle="trendline shown in red")+
+  xlab("chunk")+
+  ylab("accuracy")

\end{Sinput}
\end{Schunk}

\begin{figure}[H]
\begin{center}
\includegraphics{stream_result}
\caption {Progressive accuracy of the stream classifier}
\label{fig2}
\end {center}
\end {figure}

@@

\begin{Schunk}
\begin{Sinput}
> library(dplyr)
> library(tm)
> library(SnowballC)
> library(RColorBrewer)
> library(wordcloud)
> library(ggplot2)
> library(gridExtra)
> library(graph)
> library(Rgraphviz)
> library(RTextTools)
> df <- read.csv("leaveRemainTweets_CW.csv")
\end{Sinput}
\end{Schunk}
The 'leave' and 'remain' tweets are seperated and stored in different objects. We also check that we have captured all tweets by seperating by label (ie there a no unlabelled tweets, or any with labels outwith 'leave' or 'remain'):
\begin{Schunk}
\begin{Sinput}
> #seperate dataframes for leave and remain tweets
> leave_tweets <- df%>%
+   filter(label=="Leave")
> remain_tweets <- df%>%
+   filter(label=="Remain")
> #check we have captured all the tweets
> nrow(df)==(nrow(leave_tweets) + nrow(remain_tweets))
\end{Sinput}
\begin{Soutput}
[1] TRUE
\end{Soutput}
\end{Schunk}
It is important to ensure the dataset is balanced, ie there are a similar number of leave and remain tweets. There are more leave tweets than remain ones, but the difference isn't too great:
\begin{Schunk}
\begin{Sinput}
> nrow(leave_tweets)
\end{Sinput}
\begin{Soutput}
[1] 1254
\end{Soutput}
\begin{Sinput}
> nrow(remain_tweets)
\end{Sinput}
\begin{Soutput}
[1] 1029
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> #make wordclouds from the frequency tables
> make_wordcloud(remain$freq_tab)
\end{Sinput}
\end{Schunk}
\includegraphics{submission-029}

@@

\begin{figure}[H]
\begin{center}
\begin{Schunk}
\begin{Sinput}
> make_wordcloud(leave$freq_tab)
\end{Sinput}
\end{Schunk}
\includegraphics{submission-030}
\caption {Wordclouds for the leave tweets}
\label{fig11}
\end {center}
\end {figure}

In addition to wordclouds, we can plot the most common words for each class of tweet. This is achieve with the function below:
\begin{Schunk}
\begin{Sinput}
> #function to plot wordcounts
> plot_wordcount <- function(freq_tab,title_text){
+   ggplot(head(freq_tab,20), aes(x=word,y=freq))+
+     geom_bar(stat="identity")+
+     labs(title=title_text)+
+     theme(axis.text.x = element_text(angle = 30, hjust = 1))
+ }
> a<-plot_wordcount(all_tweets$freq_table,"most common words for all tweets")
> b<-plot_wordcount(remain$freq_table,"most common words for remain tweets")
> c<-plot_wordcount(leave$freq_table,"most common words for leave tweets")
\end{Sinput}
\end{Schunk}
The most common word for leave tweeters was 'June', suggesting many of them were focused on reinforcing the timing of the referendum - ensuring people remembered to go out and vote. 'via', 'spread' and 'word' were also common, suggesting attempts to get readers to spread the message. The general theme of many of the common words for leave tweets is of trying to increase virality and therefore increase re-tweets.\\
The most common word for remain tweeters was 'say', followed by 'stay', 'will' and 'bori[s]'. These give less of an impression of a common theme compared to the leave tweets. It is not surprising that 'Boris' is mentioned a lot by the remain tweeters since he proved to be a particularly divisive figure during the campaigning. However, the lack of common theme for leave tweets may point to an overall less coordinated campaign and may have been a contributary factor to the final result of the referendum (this is just conjecture however - it must be stressed that the dataset forms a small minority of all tweets from the campaign period).\\
As a humorous aside 'brexitthemovi[e]' was in the top 20 most common words. I don't remember this term from the campaign period but it is interesting to see such a specific term become so popular.

\begin{figure}[H]
\begin{center}
\begin{Schunk}
\begin{Sinput}
> grid.arrange(a,b,c, nrow = 3)
\end{Sinput}
\end{Schunk}
\includegraphics{submission-032}
\caption {Wordcounts for the tweets}
\label{fig10}
\end {center}
\end {figure}

@@

\begin{figure}[H]
\begin{center}
\begin{Schunk}
\begin{Sinput}
> plot(remain$tdm, term = findFreqTerms(remain$tdm, lowfreq = 10), corThreshold = 0.1,
+      weighting = T, main="word association for remain tweets")
\end{Sinput}
\end{Schunk}
\includegraphics{submission-033}
\caption {Word association for remain tweets}
\label{fig12}
\end {center}
\end {figure}

The leave tweets on the other hand show some strongly associated words. As suspected previously 'spread', 'word' and 'via' are strongly associated. This suggests a coordinated effort to increase virality of these tweets and make them more visible. 
'Take back control' is another strong grouping. This is a strong and positivley phrased phrase  which would be likely to grab and hold readers' attention (whether we agree with it or not). This contrasts with the negative phrases from the remain tweets which, rather than focusing on why readers should vote remain, seemed more to focus on why readers should \emph{not} vote leave.
Finally 'Cameron', 'Send' and 'Speech' were strongly associated. The reason for this is a little more difficult to ascertain but may relate to one of Cameron's campaign speeches or debates which generally proved to be divisive at the time.
\begin{figure}[H]
\begin{center}
\begin{Schunk}
\begin{Sinput}
> plot(leave$tdm, term = findFreqTerms(leave$tdm, lowfreq = 15), corThreshold = 0.1,
+      weighting = T, main="word association for leave tweets")
\end{Sinput}
\end{Schunk}
\includegraphics{submission-034}
\caption {Word association for leave tweets}
\label{fig12}
\end {center}
\end {figure}

@@

\begin{Schunk}
\begin{Sinput}
> #transpose the dtm to get word count for each tweet
> dtm<-make_tdm(df$text,10)
> dtm<-dtm$dtm
> #checknumber of columns used for model
> ncol(as.matrix(dtm))
\end{Sinput}
\begin{Soutput}
[1] 87
\end{Soutput}
\end{Schunk}
Using the RTextTools package, the tweets are saved in a container-type object. This automatically performs a train-test split. In this case the training set forms 70\% of the data:
\begin{Schunk}
\begin{Sinput}
> container <- create_container(dtm, df$label,trainSize=1:round(0.7*nrow(df)), testSize=(round(0.7*nrow(df))+1):nrow(df),virgin=TRUE)
> 
\end{Sinput}
\end{Schunk}
A number of classification models are trained on the data, and evaluated on the test set. RTextTools automatically creates results and analytics objects which we can use to evaluate model performance:
\begin{Schunk}
\begin{Sinput}
> #train some models and analyse the results
> models <- train_models(container,algorithms=c("SVM","BAGGING","BOOSTING","RF"))
> results <- classify_models(container, models) #can use for conf matrix
> #analytics <- create_analytics(container, results)
\end{Sinput}
\end{Schunk}
Looking at confusion matrices for each of the model types we get the following:
\begin{Schunk}
\begin{Sinput}
> print("SVM")
\end{Sinput}
\begin{Soutput}
[1] "SVM"
\end{Soutput}
\begin{Sinput}
> table(predicted=results$SVM_LABEL,actual=container@testing_codes)
\end{Sinput}
\begin{Soutput}
         actual
predicted Leave Remain
   Leave    379    270
   Remain    15     21
\end{Soutput}
\begin{Sinput}
> print("Bagging")
\end{Sinput}
\begin{Soutput}
[1] "Bagging"
\end{Soutput}
\begin{Sinput}
> table(predicted=results$BAGGING_LABEL,actual=container@testing_codes)
\end{Sinput}
\begin{Soutput}
         actual
predicted Leave Remain
   Leave    100     41
   Remain   294    250
\end{Soutput}
\begin{Sinput}
> print("Boosting")
\end{Sinput}
\begin{Soutput}
[1] "Boosting"
\end{Soutput}
\begin{Sinput}
> table(predicted=results$LOGITBOOST_LABEL,actual=container@testing_codes)
\end{Sinput}
\begin{Soutput}
         actual
predicted Leave Remain
   Leave    383    272
   Remain    11     19
\end{Soutput}
\begin{Sinput}
> print("Random Forest")
\end{Sinput}
\begin{Soutput}
[1] "Random Forest"
\end{Soutput}
\begin{Sinput}
> table(predicted=results$FORESTS_LABEL,actual=container@testing_codes)
\end{Sinput}
\begin{Soutput}
         actual
predicted Leave Remain
   Leave    105     44
   Remain   289    247
\end{Soutput}
\end{Schunk}
None of these are particularly impressive. Let's take the model with the highest accuracy (the SVM) and tune the hyperparameters. The minimum term frequency is also reduced to incorporate more features into the model training.:
\begin{Schunk}
\begin{Sinput}
> dtm<-make_tdm(df$text,2)
> dtm<-dtm$dtm
> container <- create_container(dtm, df$label,trainSize=1:round(0.7*nrow(df)), testSize=(round(0.7*nrow(df))+1):nrow(df),virgin=TRUE)
> library(e1071)
> tuned_svm <- tune.svm(x=container@training_matrix, y=container@training_codes, 
+                       validation.x = container@classification_matrix, validation.y=container@testing_codes,
+                       gamma=10^(-6:0) , cost=10^(-1:3))
> print('model accuracy = ' )
\end{Sinput}
\begin{Soutput}
[1] "model accuracy = "
\end{Soutput}
\begin{Sinput}
> 1-tuned_svm$best.performance
\end{Sinput}
\begin{Soutput}
[1] 0.5700943
\end{Soutput}
\end{Schunk}
